---
title: "p8105_hw6_jr4392"
author: "Junyi Ren"
output: github_document
---

```{r}
library(tidyverse)
library(modelr)
```

## Problem 2

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2022-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```
```{r}
weather_data_df = weather_df |>
  modelr::bootstrap(n = 5000) |>
  mutate(
    models = map(strap, \(df) lm(tmax ~ tmin + prcp, data = df) ),
    results = map(models, broom::tidy),
    rsquared = map(models, broom::glance)) |> 
  select(.id, results, rsquared) |> 
  unnest(rsquared,results) |>
  select(.id, term, estimate, r.squared) |>
   pivot_wider(
    names_from = term,
    values_from = estimate) |>
  mutate(log_β1_β2 = log(tmin * prcp)) 
```

```{r}
weather_data_df |>
  ggplot(aes(x = r.squared)) + geom_density()
```
The r squared has normal distribution, which centered at 0.92.

```{r}
weather_data_df |>
  ggplot(aes(x = log_β1_β2)) + geom_density()
```
The log($\hat{\beta_1} * \hat{\beta_2}$) has left-skewed distribution.

```{r}
ci_r_squared = quantile(pull(weather_data_df, r.squared), c(0.025, 0.975))
ci_log_β1_β2 = quantile(pull(weather_data_df, log_β1_β2), c(0.025, 0.975), na.rm = TRUE)
print(ci_r_squared)
print(ci_log_β1_β2)
```
## Problem 3

```{r}
birthweight = read_csv("data/birthweight.csv") |>
  janitor::clean_names() |>
  mutate( 
    babysex = 
      case_match(
        babysex, 
        1 ~ "male", 
        2 ~ "female"),
    babysex = as.factor(babysex),
    frace = 
           case_match(
             frace,
             1 ~ "White", 
             2 ~ "Black", 
             3 ~ "Asian", 
             4 ~ "Puerto Rican", 
             8 ~ "Other", 
             9 ~ "Unknown"),
         frace = as.factor(frace),
     malform = 
           case_match(
             malform,
             0 ~ "absent",
             1 ~ "present"),
         malform = as.factor(malform),
     mrace = 
           case_match(
             mrace,
             1 ~ "White", 
             2 ~ "Black", 
             3 ~ "Asian", 
             4 ~ "Puerto Rican", 
             8 ~ "Other"),
         mrace = as.factor(mrace)
  ) |>
  drop_na() |>
  select(-pnumlbw, -pnumsga)
```
```{r}
linear_mod = lm(bwt ~ ., data = birthweight)
bwt_mod = lm(bwt ~ babysex + delwt + ppbmi + ppwt + wtgain, data = birthweight)

birthweight |>
  add_predictions(bwt_mod, "predicted") |>
  add_residuals(bwt_mod, "residuals") |>
  ggplot(aes(x = predicted, y = residuals)) +
  geom_point() +
  labs(title = "Residuals vs. Fitted Values", x = "Fitted Values", y = "Residuals")
```

The `linear_mod` model is a linear regression model that includes all variables in the birthweight dataset. I set the `bwt_mod` model as predictors that includes only a subset of variables (babysex, delwt, ppbmi, ppwt, wtgain). 
The points are gatherd in the region of 2750-3500 fitted values and -1000-1000 residuals. 
```{r}
model_1 = lm(bwt ~ blength + gaweeks, data = birthweight)
model_2 = lm(bwt ~ bhead * blength * babysex, data = birthweight)
cv_df = 
  crossv_mc(birthweight, 100) |>
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)) |>
  mutate(
    bwt_mod  = map(train, \(df) lm(bwt ~ babysex + delwt + ppbmi + ppwt + wtgain, data = df)),
    model_1  = map(train, \(df) lm(bwt ~ blength + gaweeks, data = df)),
    model_2  = map(train, \(df) lm(bwt ~ bhead * blength * babysex, data = df))) |> 
  mutate(
    rmse_bwt_mod = map2_dbl(bwt_mod, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_model_1 = map2_dbl(model_1, test, \(mod, df) rmse(model = mod, data = df)),
    rmse_model_2 = map2_dbl(model_2, test, \(mod, df) rmse(model = mod, data = df)))
```


```{r}
cv_df |> 
  select(starts_with("rmse")) |> 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") |> 
  mutate(model = fct_inorder(model)) |> 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```
Using RMSE as a way to compare the three models, and the plot above shows the distribution of RMSE values for each candidate model. However, the model I set was not optimal.


